Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-28 paper/main.tex
adjust plan

\noindent Generally
\begin{itemize}
    \item Todo's are mostly comments and can be deleted if issue is solved by
        current phrasing
    \item Lescroart is just a small footnote in pPPA vs. aPPA in discussion
        (problem to write more about the paper: it is voxel-wise encoding which
        does not tell a lot about increased vs. decreased activation; "crafted"
        stimuli: 45 min of 850 scenes, made from 33 backgrounds + 2-3 objects
        drawn from pool of 440 objects
    \item maybe "do something with" dice-index
    \item position of figures and tables is very odd now but probably does not
        matter
\end{itemize}

@@

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI and annotation data, analysis scripts to generate the results as well
as results are available in the [NAME] repository, [PERSISTENT WEB LINK],
accessible as Datalad (RRID:SCR\_003931) datasets.

>>>>

\noindent Generally
\begin{itemize}
    \item Todo's are mostly comments and can be deleted if issue is solved by
        current phrasing
    \item https://gin.g-node.org/; upload; datacite.yml; readme; reserve \&
        cite DOI in data availability section
    \item Lescroart is just a small footnote in pPPA vs. aPPA in discussion
        (problem to write more about the paper: it is voxel-wise encoding which
        does not tell a lot about increased vs. decreased activation; "crafted"
        stimuli: 45 min of 850 scenes, made from 33 backgrounds + 2-3 objects
        drawn from pool of 440 objects
    \item maybe "do something with" dice-index
\end{itemize}

@@

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI and annotation data, analysis scripts to generate the results as well
as results are available in the gin repository,
\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}, accessible as Datalad (RRID:SCR\_003931) datasets.
